\vspace{-0.25em}\thetitle

### 2009-07-23 paper.tex
...

This property allows us to visualize the approximate structure of $X$ using initial columns of $US$.
However, the most significant feature of any vector in this representation is its magnitude, while we are interested in the direction of vectors:
points with the same direction lie in the same one-dimensional subspace.
To visualize direction while eliminating distance, we project all data points radially onto the hyperplane in which all points have coordinates summing to unity.\projectionnote
\Figure{svd} shows scatter plots of the most significant two projected \caps{SVD} coordinates for four different traces.
The original coordinates of this data encode the packet size distributions, inter-packet interval distributions, \caps{IP} protocol numbers, and port numbers for a sample of 5000 flows for each trace.
The exact details of how the linear representation encodes these features will be discussed in \Section{methodology}.

\begin{figure}[!t]
\vspace{0.5em}
\begin{center}
\subfloat[\footnotesize{IETF 60}]{\includegraphics[width=1.6in]{svd/ie60}}
\subfloat[\footnotesize{IETF 67}]{\includegraphics[width=1.6in]{svd/ie67}}
\subfloat[\footnotesize{SIGCOMM 2004}]{\includegraphics[width=1.6in]{svd/sc04}}
\subfloat[\footnotesize{UCSD}]{\includegraphics[width=1.6in]{svd/ucsd}}
\caption{SVD scatter plots for various traces.} 
\fig{svd}
\end{center}
\vspace{-2em}
\end{figure}

Linear structure is clearly visible in \Figure{svd}:
the points are heavily concentrated on low-dimensional subspaces.
Because of the projection step of our process, points concentrated along a one-dimensional subspace appear as dark ``spots'' where many points have been plotted;
points concentrated along a two-dimensional subspace appear as lines;
points falling along subspaces of three or more dimensions appear as ``smears.''

>>>>

This property allows us to visualize the approximate structure of $X$ using initial columns of $US$.
We are, however, for the moment only interested in direction not magnitude:
vectors with the same direction lie in the same one-dimensional subspace.
To visualize direction while eliminating distance, we project all data points onto the unit-sum hyperplane through the origin.\projectionnote
\Figure{svd} shows scatter plots of the most significant two projected \caps{SVD} coordinates for four different traces of network traffic.
The original data encodes packet size distributions, inter-packet interval distributions, \caps{IP} protocol numbers, and port numbers for a sample of 5000 flows from each trace.
The exact details of how the linear representation encodes these features will be discussed in \Section{methodology}.

\begin{figure}[!t]
\vspace{0.5em}
\begin{center}
\subfloat[\footnotesize{IETF 60}]{\includegraphics[width=1.6in]{svd/ie60}}
\subfloat[\footnotesize{IETF 67}]{\includegraphics[width=1.6in]{svd/ie67}}
\subfloat[\footnotesize{SIGCOMM 2004}]{\includegraphics[width=1.6in]{svd/sc04}}
\subfloat[\footnotesize{UCSD}]{\includegraphics[width=1.6in]{svd/ucsd}}
\caption{SVD scatter plots for various traffic traces.} 
\fig{svd}
\end{center}
\vspace{-2em}
\end{figure}

Linear structure is clearly visible in \Figure{svd}:
the points are heavily concentrated on low-dimensional subspaces.
Because of the projection step of our process, points concentrated along a one-dimensional subspace appear as dark ``spots'' where many points have been plotted;
points concentrated along a two-dimensional subspace appear as lines;
points falling near subspaces of more dimensions appear as ``smears.''
